### 2016-04-04 docs/ms_communitySynchrony_PREPRINT.tex
adds peer review disclosure to preprint

\usepackage{setspace}
\usepackage{todonotes}
\usepackage{color}
\usepackage{rotating}

@@

\begin{singlespace}

@@

Ecosystems are being transformed by species extinctions (Cardinale et
al. 2012), changes in community composition (Vellend et al. 2013,
Dornelas et al. 2014), and anthropogenic environmental change (Vitousek
et al. 1997), impacting the provisioning and stability of ecosystem
services (Loreau et al. 2001, Hooper et al. 2005, Rockstrom et al.
2009). Experiments have provided compelling evidence that decreases in
species richness will decrease productivity (Tilman et al. 2001) and the
temporal stability of productivity (Tilman et al. 2006, Hector et al.
2010). The stabilizing effect of species richness stems from individual
species responding to environmental fluctuations (environmental
stochasticity), or fluctuating asynchronously because of random chance
events (demographic stochasticity). (Isbell et al. 2009, Hector et al.
2010, {{de Mazancourt}} et al. 2013). Species richness affects synchrony
because larger species pools are more likely to contain species that
respond disimilarly to environmental conditions (Yachi and Loreau 1999),
implying that species losses will reduce ecosystem stability. Even
without species losses, abiotic homogenization can weaken compensatory
dynamics and, in turn, decrease temporal stability of ecosystem
functioning (Hautier et al. 2014). Predicting the impacts of global
change requires a mechanistic understanding of species synchrony in
natural settings.

>>>>

\usepackage{setspace}
\usepackage{todonotes}
\usepackage{color}
\usepackage{rotating}
\usepackage{fancyhdr}
\pagestyle{fancy}
\chead{\color{red}THIS MANUSCRIPT HAS NOT UNDERGONE PEER REVIEW}
\lhead{}
\rhead{}

@@

\thispagestyle{fancy}
\begin{singlespace}

@@

Ecosystems are being transformed by species extinctions (Cardinale et
al. 2012), changes in community composition (Vellend et al. 2013,
Dornelas et al. 2014), and anthropogenic environmental change (Vitousek
et al. 1997), impacting the provisioning and stability of ecosystem
services (Loreau et al. 2001, Hooper et al. 2005, Rockstrom et al.
2009). Experiments have provided compelling evidence that decreases in
species richness will decrease productivity (Tilman et al. 2001) and the
temporal stability of productivity (Tilman et al. 2006, Hector et al.
2010). The stabilizing effect of species richness stems from individual
species responding to environmental fluctuations (environmental
stochasticity), or fluctuating asynchronously because of random chance
events (demographic stochasticity) (Isbell et al. 2009, Hector et al.
2010, {{de Mazancourt}} et al. 2013). Species richness affects synchrony
because larger species pools are more likely to contain species that
respond disimilarly to environmental conditions (Yachi and Loreau 1999),
implying that species losses will reduce ecosystem stability. Even
without species losses, abiotic homogenization can weaken compensatory
dynamics and, in turn, decrease temporal stability of ecosystem
functioning (Hautier et al. 2014). Predicting the impacts of global
change requires a mechanistic understanding of species synchrony in
natural settings.
